---
title: "Week 6 Exercise: R Markdown"
author: "Wenhui Zeng"
date: "08/03/2016"
output: pdf_document
---

Edit the YAML header (above) to reflect your name and today's date, then procede to edit the rest of this document according the directions below. Submit both a .Rmd docmunt and a fully typset PDF.

#Exercise 1: Headers

Edit this R Markdown script so that each exercise header (e.g. "Exercise 1" above) gets typset as a level 1 header.

Exercise 2: Font

Make one word in the sentence **bold**, one word *italicized*, one word ***bold-italicized***, and one word ~~strike-through~~.

Exercise 3: Lists

Create an enumerated list of your top 5 favorite movies.
1. favorite
    1. Harry Porter
    2. Brave
    3. Up
    4. Finding Dory
    5. Frozen


Create an unordered list of 3 things about R that annoy you.
* Unfavor of R
    * Always install something
    * Always update
    * There is no professional certification of R. 

Exercise 4: Web-links

Link the phrase "R Studio cheat sheets" to the following URL: https://www.rstudio.com/resources/cheatsheets/
[R Studio cheat sheets][M]
[M]:https://www.rstudio.com/resources/cheatsheets/

Exercise 5: R-chunk with echo

Wrap the following R code into a "chunk" that displays both the input and evaluated output.

```{r}
library(ISwR)
data(red.cell.folate)
summary(red.cell.folate)
```

Exercise 6: R chunk with results = "as.is"

What happens if you display the summary with the chunk option, results="as.is"

```{r, results='asis'}
summary(red.cell.folate)
```

Exercise 7: R-chunk without echo

Wrap the folloing into a chunk that shows a boxplot of folate by ventilation, but does not "echo" the input commands.

```{r, echo=F}
library(ggplot2)
ggplot(data = red.cell.folate, aes(x = ventilation, y = folate)) + geom_boxplot()
```

Exercise 8: print(xtable(...))

Write one more expression to the following R script that prints an xtable of the folate.aov.summary object, then enclose all lines into a chunk that displays a typeset table, but not the input code.


```{r, echo=FALSE, results='asis'}
library(xtable)
library(ISwR)
folate.aov.summary <- summary(aov(folate ~ ventilation, data = red.cell.folate))
print(xtable(folate.aov.summary), type = "latex", comment = FALSE)
```

Exercise 9: Inline results

Pull the F statistic, degrees of freedom, and p-value from the folate.aov.summary object in a chunk that is not echoed, and then display those statistics inline here.


```{r, echo=F, include=F}
library(xtable)
library(ISwR)
folate.aov.summary <- summary(aov(folate ~ ventilation, data = red.cell.folate))
f <- folate.aov.summary[[1]][1,4]
df1 <- folate.aov.summary[[1]][1,1]
df2 <- folate.aov.summary[[1]][2,1]
p <- folate.aov.summary[[1]][1,5]
attributes(p) <- NULL 
```
($F_{`r df1`, `r df2`} = `r f`, p = `r p`):






